Dynein project log

### 2016-12-30 thesis_stuff/thesis_stuff.tex
Add spring constant finding stuff to thesis_stuff.tex.

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & notes & outcome\\\hline
    22.1 & 11.1 & 5000 & 5000 & 23.0 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability is about $10^{-150}$, spring constants too high to allow unbinding\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & trying to find good springs for binding & unbinding probability oscillates around $10^{-9}$, seems good will explore more\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.023 & 0.023 & 0.023 & trying to find good springs for binding & not rigid enough, kneels over and collides with MTs\\\hline
  \end{tabular}
\end{center}

>>>>

\begin{center}
  \begin{tabular}{| l | l | l | l | l | l | l | p{3cm} | p{5cm} |}
    \hline
    Ls & Lt & kb & kub & cm & cb & ct & $\Big<P(\mbox{unbind})\Big>$  & errors\\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.02 & 0.02 & 0.02 & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.11 & 0.11 & 0.11 & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.18 & 0.18 & 0.18 & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.23 & 0.23 & 0.23 & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 0.58 & 0.58 & 0.58 & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.16 & 1.16 & 1.16 & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 1.74 & 1.74 & 1.74 & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.32 & 2.32 & 2.32 & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 2.90 & 2.90 & 2.90 & & \\\hline
    22.1 & 11.1 & 5000 & 5000 & 3.49 & 3.49 & 3.49 & & \\\hline
  \end{tabular}
\end{center}

findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-32786885246,cm-0.0232786885246,ct-0.0232786885246,T-310.15.out
findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-6393442623,cm-0.116393442623,ct-0.116393442623,T-310.15.out
findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-6229508197,cm-0.186229508197,ct-0.186229508197,T-310.15.out
findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-2786885246,cm-0.232786885246,ct-0.232786885246,T-310.15.out
findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-1967213115,cm-0.581967213115,ct-0.581967213115,T-310.15.out
findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-393442623,cm-1.16393442623,ct-1.16393442623,T-310.15.out
findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-590163934,cm-1.74590163934,ct-1.74590163934,T-310.15.out
findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-786885246,cm-2.32786885246,ct-2.32786885246,T-310.15.out
findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-983606557,cm-2.90983606557,ct-2.90983606557,T-310.15.out
findnotnansprings__ls-22.1,lt-11.2,k_b-5000,cb-180327869,cm-3.49180327869,ct-3.49180327869,T-310.15.out
